sensiAnPaper1All

### 2015-07-14 sensiAnPaper1All.Rmd
limited trees

    #dev.off()
    savePlot(paste0(outFolder,"tree",treeResponse,".png"), type='png')     
  }

>>>>

    #dev.off()
    #savePlot(paste0(outFolder,"tree",treeResponse,".png"), type='png')
    savePlot(paste0(outFolder,"tree",treeResponse,".jpg"), type='jpg')

    #trying to limit num levels a different way using maxdepth
    tree <- rpart::rpart(as.formula(paste(treeResponse,"~",treePredictorString)), data = treeInput, method = 'class', maxdepth=3) 
    #adds in no. scenarios correctly and incorrectly classified
    prp(tree, extra=1, varlen = 10, main=treeResponse)
    savePlot(paste0(outFolder,"tree",treeResponse,"depth3.jpg"), type='jpg')

  }
